\textsf{Are large language models superhuman chemists?}

### 2024-10-20 src/tex/ms.tex

\begin{figure}[!htb]
    \centering
    \includegraphics[width=\textwidth]{figures/cb_corpus_v3.pdf}
    \caption{\textbf{Distribution of topics and required skills.} This circular plot illustrates the distribution of questions across various chemistry topics, along with the primary skills required to address them. The topics were manually classified, showing a varied representation across different aspects of chemistry. Each topic is associated with a combination of three key skills: Calculation, Reasoning, and Knowledge, as indicated by the colored bars. \chembench samples diverse topics and diverse skills, setting a high bar for \glspl{llm} to demonstrate human-competitive performance across a wide range of chemistry tasks.}
    \label{fig:corpus}
\end{figure}

@@

% \begin{figure}[!h]
%     \centering
%     \includegraphics{figures/confidence_vs_performance_overall.pdf}
%     \caption{\textbf{Relationship between confidence of the model in the answer and correctness.} For this analysis, we used verbalized confidence estimates from the model. We prompted the models to return a confidence score on an ordinal scale to obtain those estimates. We then plot the correctness of the answers (which is calculated as the mean value of all answers being either correct (1) or incorrect (0)) against the confidence score.
%         The stripplots show the individual data points, a strong density indicating a higher number of points. The lines show the mean, and the error bars show the standard error of the mean. The figure shows that the reliability of the confidence estimates varies widely across models. While the ones for GPT-4 and Claude 2 are not particularly reliable, the ones for Claude 3 follow the expected trend better.}
%     \label{fig:confidence_vs_performance}
%     \script{joint_analysis_confidence_performance.py}
% \end{figure}

@@

\paragraph{Question selection} \label{sec:subset-selection}
Rewrite.

>>>>

\begin{figure}[!htb]
    \centering
    \includegraphics[width=\textwidth]{figures/CB_OVERVIEW_FIG_V1.pdf}
    \caption{\textbf{Distribution of topics and required skills.} This circular plot illustrates the distribution of questions across various chemistry topics, along with the primary skills required to address them. The topics were manually classified, showing a varied representation across different aspects of chemistry. Each topic is associated with a combination of three key skills: Calculation, Reasoning, and Knowledge, as indicated by the colored bars. \chembench samples diverse topics and diverse skills, setting a high bar for \glspl{llm} to demonstrate human-competitive performance across a wide range of chemistry tasks.}
    \label{fig:corpus}
\end{figure}

@@

 \begin{figure}[!h]
     \centering
     \includegraphics[width=\textwidth]{figures/model_confidence_performance.pdf}
     \caption{\textbf{Calibration and distribution of confidence estimates.} For this analysis, we used verbalized confidence estimates from the model. We prompted the models to return a confidence score on an ordinal scale to obtain those estimates. }
     \label{fig:confidence_vs_performance}
     \script{confidence_estimate.py}
 \end{figure}

@@

\input{sections/human_subset_selection.tex}
